### 2017-04-05 paper/evaluation.tex
added missing table

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default (see
Section~\ref{sec:rqC-1}). To measure the overall speedup obtained from
parallel execution, we compared the elapsed time in the default
execution (parallelization enabled) and re-executed the tests
sequentially.
To enforce sequential execution,
\Fix{elaborar metodologia}
\Fix{dizer que verificamos que a execucao eh consistente e o
outcome eh igual ao da execucao padrao}.

@@

% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{\Fix{This is a COPY from the previous table!}}
    \label{tab:inspection-table}
\end{figure}

%% \begin{figure}[ht!]
%%     \centering
%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
%%         \toprule
%%         \multirow{2}{*}{Group} %1st row, 1st cell
%%             & \multirow{2}{*}{\# \pomf{}}
%% 	    & \# \pomf{} matched\\
%%         % 2nd row - empty cell
%%             & % empty cell
%%             & / total\\%
%%         \midrule%
%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
%%         \midrule%
%%         Total % last row, first cell
%%             & \pomMedLong{}
%%             & \numProjectsPar{} / \numMedLong{}\\%
%%         \bottomrule%
%%     \end{tabular*}
%%     \caption{Presence of parallelization settings in build files: the
%%     first column indicates the group of projects according to their
%%     time cost; the second column is the subset of files with parallelization
%%     keywords; the last column indicates the ratio of projects with
%%     parallelism support.}
%%     \label{tab:inspection-table} 
%% \end{figure}
%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
%% identified above, we investigated further the \numPomMatched{}
%% build files with parallel settings.  We analyzed the support and
%% distribution of parallel modes from this subset of projects. To
%% calculate the distribution of parallel modes, we considered only the
%% presence of the mode in at least one of the project settings.  Recall
%% that a build file may contain more than one parallel setting and a
%% project may contain several sub-modules with build files.  In case the
%% value of a parallel option is resolved dynamically (\eg, via
%% command-line argument or system variable) we compute all modes related
%% to the option. For instance, depending on the value, the
%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
%% \Fix{Missing conclusion: Fork the most used configuration}
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
%%     identified statically in a subset of \numProjectsPar{} projects.
%%     A project may have support to more than one parallel mode.}
%% \end{figure}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that parallelism features are underused by default given that
      only \percentParallel{} of projects  (5 out of \numMedLong)
      supports parallel execution of test suites without any extra
      parameter.}
  \end{minipage}
}
\end{center}

>>>>

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default (see
Section~\ref{sec:rqC-1}). To measure the overall speedup obtained from
parallel execution, we compared the elapsed time in the default
execution (parallelization enabled) and re-executed the tests
sequentially.  To enforce sequential execution, we modified the
existing configurations. Also, we verified that, for each project,
both executions (\ie, default and sequential) are consistent and
produce the same outcome. To compute the speedup, we divide the
sequential time by the default execution. For instance, for a project
that runs in $10m$ sequentially and runs in $5m$ in the default execution,
the speedup is two.

\begin{figure}[ht!]
\centering
\resizebox{.48\textwidth}{!}{%
\begin{tabular}{lllll}
\toprule
Group & Subject & T$_{\text{p}}$ & T$_{\text{s}}$ & Speedup\\%
\midrule%
Long   & JenkinsCI Gerrit Trigger Plugin & \Fix{?} & \Fix{?} & \Fix{?}\\%
Medium & Apache Logging Log4J2           & \Fix{?} & \Fix{?} & \Fix{?}\\%
Medium & Jankotek MapDB                  & \Fix{?} & \Fix{?} & \Fix{?}\\%
Medium & Javaslang                       & \Fix{?} & \Fix{?} & \Fix{?}\\%
Medium & Jcabi Github                    & \Fix{?} & \Fix{?} & \Fix{?}\\%
\bottomrule%
\end{tabular}}
\caption{\Fix{Comparacao de tempo sequencial e paralelo}}
\label{tab:speedup}
\end{figure}

Figure~\ref{tab:speedup} summarizes our findings.
\Fix{falar sobre o resultado geral dos speedups - elaborar menor e
maior speedup}

@@

% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{\Fix{This is a COPY from the previous table!}}
    \label{tab:inspection-table}
\end{figure}
%% \begin{figure}[ht!]
%%     \centering
%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
%%         \toprule
%%         \multirow{2}{*}{Group} %1st row, 1st cell
%%             & \multirow{2}{*}{\# \pomf{}}
%% 	    & \# \pomf{} matched\\
%%         % 2nd row - empty cell
%%             & % empty cell
%%             & / total\\%
%%         \midrule%
%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
%%         \midrule%
%%         Total % last row, first cell
%%             & \pomMedLong{}
%%             & \numProjectsPar{} / \numMedLong{}\\%
%%         \bottomrule%
%%     \end{tabular*}
%%     \caption{Presence of parallelization settings in build files: the
%%     first column indicates the group of projects according to their
%%     time cost; the second column is the subset of files with parallelization
%%     keywords; the last column indicates the ratio of projects with
%%     parallelism support.}
%%     \label{tab:inspection-table} 
%% \end{figure}
%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
%% identified above, we investigated further the \numPomMatched{}
%% build files with parallel settings.  We analyzed the support and
%% distribution of parallel modes from this subset of projects. To
%% calculate the distribution of parallel modes, we considered only the
%% presence of the mode in at least one of the project settings.  Recall
%% that a build file may contain more than one parallel setting and a
%% project may contain several sub-modules with build files.  In case the
%% value of a parallel option is resolved dynamically (\eg, via
%% command-line argument or system variable) we compute all modes related
%% to the option. For instance, depending on the value, the
%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
%% \Fix{Missing conclusion: Fork the most used configuration}
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
%%     identified statically in a subset of \numProjectsPar{} projects.
%%     A project may have support to more than one parallel mode.}
%% \end{figure}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that parallelism features are underused by default given that
      only \percentParallel{} of projects  (5 out of \numMedLong)
      supports parallel execution of test suites by default and
      \Fix{?\%} (\Fix{y} out of \numMedLong{}) require additional
      parameters to enable these features.}
  \end{minipage}
}
\end{center}
